---
title: "STAT 585X Lab 1"
author: Amy Crawford, Katie Will, and Katherine Goode
output: pdf_document
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
```

# Building a Book

Unfortunately, our group was not able to build the book completely. While trying to build the tex file, the error we encountered was "input Inconsolata' failed to make Inconsolata.tfm". This error occured while running the system() function. We understand that this is a font used in the book. We tried downloading the inconsolata font onto our Mac machines, but the file type that came through was a .otf file intead of the desired .tfm file. How do we download a .tfm font file onto our Mac machines to be used to build a tex file?


# US Weather Stations

Not sure what the best thing is to do for setting the working directory in this document. This is just the
directory where I have the data saved on my computer...
```{r, message = FALSE}
setwd("~/Desktop/STAT 585X/Labs/Lab 1/ushcn.v2.5.5.20170119")
```

```{r, message = FALSE}
library(tidyverse)
library(ggplot2)
```

```{r}
tmax <- function(stationid){
                      file <- paste("USH00", stationid,".raw.tmax", sep = "")
                      temps <- read_fwf(file, col_positions = fwf_positions(
                                start=c( 1,13, rep(16+9*0:11, each=4) + c(1,7,8,9)), 
                                end  =c(11,16, rep(16+9*0:11, each=4) + c(6,7,8,9))))
                      names(temps) <- c("Station", "Year", 
                                        paste0(rep(c("Value","DMflag", "QCflag",
                                                     "DSflag"), 12), 
                                               rep(1:12, each=4)))
                      temps$Value1 <- replace(temps$Value1, temps$Value1 == -9999, NA)
                      temps$Value2 <- replace(temps$Value2, temps$Value2 == -9999, NA)
                      temps$Value3 <- replace(temps$Value3, temps$Value3 == -9999, NA)
                      temps$Value4 <- replace(temps$Value4, temps$Value4 == -9999, NA)
                      temps$Value5 <- replace(temps$Value5, temps$Value5 == -9999, NA)
                      temps$Value6 <- replace(temps$Value6, temps$Value6 == -9999, NA)
                      temps$Value7 <- replace(temps$Value7, temps$Value7 == -9999, NA)
                      temps$Value8 <- replace(temps$Value8, temps$Value8 == -9999, NA)
                      temps$Value9 <- replace(temps$Value9, temps$Value9 == -9999, NA)
                      temps$Value10 <- replace(temps$Value10, temps$Value10 == -9999, NA)
                      temps$Value11 <- replace(temps$Value11, temps$Value11 == -9999, NA)
                      temps$Value12 <- replace(temps$Value12, temps$Value12 == -9999, NA)
  return(temps)
}
```

```{r, message = FALSE}
data <- tmax(132999)
new.data <- gather(data, key = "Month", value = "Temp_Max", starts_with("Value"))
new.data$Month <- as.numeric(gsub("Value", "", new.data$Month))
max(new.data$Year); min(new.data$Year)
```

```{r, fig.width = 13, fig.height = 6, message = FALSE}
ggplot(new.data, aes(x = Year, Temp_Max/100)) + 
  geom_point() +
  facet_wrap( ~ Month, nrow = 1) +
  scale_x_continuous(breaks=seq(1900, 2000, 50)) + 
  labs(y = "Maximum Temperature")
```

Above is a plot of the maximum temperatures each month at station 132999 between the years of 1899 and 2016. It is easy to see the increasing then decreasing trend in temperatures across the months, with the temperatures peaking in July/August. The variation in maximum temperatures seems to be the greatest in the colder months. When we examine each month separatly, we don't see a clear increasing (or decreasing) trend across the years. 
